---
title: "Conceptual metaphor and graphical convention influence the interpretation of line graphs"
author: "Greg Woodin, Bodo Winter, and Lace Padilla"
date: "10/12/2018"
output:
  pdf_document:
    toc: yes
    toc_depth: 4
  word_document:
    toc: yes
    toc_depth: 4
  html_document:
    highlight: tango
    number_sections: yes
    theme: yeti
    toc: yes
    toc_depth: 4
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This is the code used to identify the valenced quantities used in the graphs in 'Conceptual metaphor and graphical convention influence the interpretation of line graphs'.

Load tidyverse and open list of valence norms in ascending order of mean valence:

```{r list, message = FALSE}

library(tidyverse)
(df <- arrange(read_csv('../data/valence_list.csv'), V.Mean.Sum))

```

Find 20 most negatively valenced words in dataset:

```{r positive}

filter(df[1:20, ])

```

Find 20 most positively valenced words in dataset:

```{r negative}

filter(df[13895:13915, ]) %>% arrange()

```

Find mean standard deviation:

```{r mean_SD}

round(mean(df$V.SD.Sum), 2)

```

Find SD of words chosen for experimental stimuli (vacation days, murders):

```{r SD_stimuli}

df %>% filter(Word == 'vacation') %>% with(mean(V.SD.Sum))
df %>% filter(Word == 'murder') %>% with(mean(V.SD.Sum))

```

